Interactive dashboard to monitor the COVID-19 outbreak

### 2022-05-06 manuscript_covid19dashboard.Rmd
Updated

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

>>>>

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(ceylon)
library(tidyverse)
library(sf)
#install.packages("cartogram")
library(cartogram)
```

@@

```{r, comment=NA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distribution of COVID19 Cases by Districts Plotted on a Single Panel"}
library(covid19srilanka)
library(tidyverse)
library(patchwork)
data("district.wise.cases")
f1 <- ggplot(district.wise.cases, aes(
  x=Date, y=Count,  col=District)) + geom_line() + ggtitle("A")

```

```{r, comment=NA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distribution of COVID19 Cases by Districts Plotted on a Single Panel", fig.height=10, fig.width=10}
library(covid19srilanka)
library(tidyverse)
data("district.wise.cases")
f2 <- ggplot(district.wise.cases, aes(
  x=Date, y=Count)) + geom_line() + 
  facet_wrap(vars(District), scale="free", ncol=5) + ggtitle("B")
f1/f2
```

```{r, echo=FALSE, comment=NA, message=FALSE, warning=FALSE}
library(viridis)
library(patchwork)
# Get District wise data 
District_Covid <- district.wise.cases
District_Covid <-District_Covid[order(as.Date(District_Covid$Date, format="%Y-%m-%d")), ]

# Get total count for each district
Last_day <- District_Covid %>%
  filter(Date == max(District_Covid$Date))

Covid <- Last_day %>%
  mutate(District = case_when(
    District == "Kurunagala" ~ "Kurunegala",
    TRUE ~ District
  ))

Covidnew <- Covid %>%
  mutate(parents = "Confirmed")

i <- 1:length(District_Covid$District)
District_Covid$daily <- District_Covid$Count[i+26] - District_Covid$Count[i]
District_Covid$Date <- as.Date(District_Covid$Date)
District_Covid <- head(District_Covid, -26)

District_Covid_new <- District_Covid %>%
  arrange(Count) %>%
  mutate(District = fct_inorder(factor(District, ordered = TRUE)))

p1 <- ggplot(District_Covid_new, aes(Date, District)) + 
           geom_tile(aes(fill = daily))+
           scale_fill_viridis(option = "magma")+ 
           scale_x_date(date_breaks = '1 week', date_labels = "%d-%b-%Y") + ggtitle("A")
```

```{r, echo=FALSE,fig.cap="(A) Global View of Distribution of COVID19 Cases by DIstricts, (B) Local View of Distribution of COVID19 Cases by Districts", fig.width=10, fig.height=10}

cov_District <- as.data.frame(District_Covid)

District <- c(District_Covid$District[1:26])
data <- cov_District

# Apply min-max transformation for each district separately
covid <- function(data, District){
  results <- list(1:26)
  for(i in 1: length(District)){
    x <- filter(data, District == District[i])
    j <- 1:(nrow(data)/26)
    y <- x$daily
    x$min_max <-(y[j] - min(y))/(max(y) - min(y))
    results[[i]] <- x
  }
  return(results)
}

Data <- covid(data, District)
District_data <- do.call(rbind, Data)

District_Covid_new_1 <- District_data %>%
  arrange(Count) %>%
  mutate(District = fct_inorder(factor(District, ordered = TRUE)))

p2 <- ggplot(District_Covid_new_1, aes(Date, District)) + geom_tile(aes(fill = min_max)) + scale_fill_viridis(option = "magma") + scale_x_date(date_breaks = '1 week', date_labels = "%d-%b-%Y") + ggtitle("B")

p1/p2
```

```{r, comment=NA, message=FALSE, warning=FALSE}

Last_day <- District_Covid %>%
  filter(Date == max(District_Covid$Date))

Covid <- Last_day %>%
  mutate(District = case_when(
    District == "Kurunagala" ~ "Kurunegala",
    TRUE ~ District
  ))

Covidnew <- Covid %>%
  mutate(parents = "Confirmed")

SL <- district
SL$DISTRICT <- str_to_title(SL$DISTRICT)
colnames(SL) <- c("geometry", "District", "status", "population")

Covid_SL <- left_join(SL, Covid, by = c("District"))

Ampara <- Covid%>%
  filter(District %in% c("Kalmunai","Ampara" ))
newcount <- Ampara$Count %>%
  sum()

Covid_SL <- Covid_SL %>%
  filter(!(District == "[unknown]")) %>%
  filter(!(District == "Kalmunai")) %>%
  mutate(Count = ifelse(District == "Ampara", newcount, Count))

m1 <- ggplot(Covid_SL) + geom_sf(aes(fill = Count, text = paste('District:', District)), show.legend = TRUE) + 
  scale_fill_viridis()+
  theme(axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank()) + ggtitle("A")

Covid_SL <- Covid_SL[-c(1), ]
dorl <- cartogram_dorling(Covid_SL, weight = "population")%>%
  st_as_sf()

m2 <- ggplot(dorl)+
  geom_sf(data = Covid_SL)+
  geom_sf(aes(fill = Count, text = paste('District:', District)))+
   scale_fill_viridis()+
  theme(axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank()) + ggtitle("B")

m1|m2

```

### 2022-05-06 manuscript_covid19dashboard.tex
Updated

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/1} \caption{Johns Hopkins University COVID-19 Dashboard}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.35in]{Images/2} \caption{WHO COVID-19 Dashboard}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/3} \caption{COVID-19 Surveillance Dashboard}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.39in]{Images/4} \caption{Corona cases per Municipality in Belgium Dashboard}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.46in]{Images/5} \caption{COVID-19 dashboard for England}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.47in]{Images/6} \caption{New Zealand COVID-19 Dashboard}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.33in]{Images/7} \caption{COVID-19 Dashboard for Pakistan}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.47in]{Images/8} \caption{COVID-19 in Canada dashboard}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/9} \caption{India COVID-19 Dashboard}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.12in]{Images/10} \caption{Italy COVID-19 Dashboard}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.35in]{Images/11} \caption{Jamaica COVID-19 Dashboard}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.25in]{Images/12} \caption{GCI COVID-19 Dashboard for Russia}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.4in]{Images/13} \caption{COVID-19 Live Situational Analysis Dashboard of Sri Lanka}\label{fig:unnamed-chunk-13}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.46in]{Images/14} \caption{COVID 19 ZA South Africa Dashboard}\label{fig:unnamed-chunk-14}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.33in]{Images/15} \caption{Robert Koch-Institute COVID-19 dashboard for German}\label{fig:unnamed-chunk-15}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Distribution of COVID19 Cases by Districts Plotted on a Single
Panel}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{(A) Global View of Distribution of COVID19 Cases by DIstricts,
(B) Local View of Distribution of COVID19 Cases by Districts}
\end{figure}

\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-5-1.pdf}

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/1} \caption{Johns Hopkins University COVID-19 Dashboard}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.35in]{Images/2} \caption{WHO COVID-19 Dashboard}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/3} \caption{COVID-19 Surveillance Dashboard}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.39in]{Images/4} \caption{Corona cases per Municipality in Belgium Dashboard}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.46in]{Images/5} \caption{COVID-19 dashboard for England}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.47in]{Images/6} \caption{New Zealand COVID-19 Dashboard}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.33in]{Images/7} \caption{COVID-19 Dashboard for Pakistan}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.47in]{Images/8} \caption{COVID-19 in Canada dashboard}\label{fig:unnamed-chunk-13}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.42in]{Images/9} \caption{India COVID-19 Dashboard}\label{fig:unnamed-chunk-14}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.12in]{Images/10} \caption{Italy COVID-19 Dashboard}\label{fig:unnamed-chunk-15}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.35in]{Images/11} \caption{Jamaica COVID-19 Dashboard}\label{fig:unnamed-chunk-16}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.25in]{Images/12} \caption{GCI COVID-19 Dashboard for Russia}\label{fig:unnamed-chunk-17}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.4in]{Images/13} \caption{COVID-19 Live Situational Analysis Dashboard of Sri Lanka}\label{fig:unnamed-chunk-18}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.46in]{Images/14} \caption{COVID 19 ZA South Africa Dashboard}\label{fig:unnamed-chunk-19}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8.33in]{Images/15} \caption{Robert Koch-Institute COVID-19 dashboard for German}\label{fig:unnamed-chunk-20}
\end{figure}
